Pillar 1 - Student Topic Profile

### 2019-04-15 Pillar 1 - Topic Profile.Rmd
grade prediction

```{r load}
load("App/Recommender System/topic_model_gb.RDATA")
load("Output/data_pillar_1.RDATA")
load("Output/d_transcript_cum.RDATA")
load("Output/course_current.RDATA")

@@

beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)
View(beta)
```

@@

```{r}
d_transcript_augmented <- d_transcript_augmented %>%

@@

```{r}
student_GPA <- d_transcript_augmented %>%

@@

# Join student TP and GPA
```{r d_TP_cum}
student_profile <- d_transcript_augmented %>%

@@

  left_join(student_TP , by = c("Student ID", "time"))
```

@@

```{r}
fit_lasso <- tibble(target = course_target) %>%

@@

```{r}
fit_lasso <- fit_lasso %>%

@@

  # Best model
  mutate(
    intercept  = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["a0"]][..2]),
    coefi      = list(m_lasso, lambda_min) %>% pmap(coef), # clearer output than pmap_dbl(~ ..1[["beta"]][,..2])
    df         = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["df"]][..2]),
    dev_null   = m_lasso %>% map_dbl(~ .[["nulldev"]]),
    dev_left   = list(m_lasso, index_best) %>% pmap_dbl(~deviance.glmnet(..1)[..2]),
    dev_unexpl = dev_null - dev_left,
    dev_ratio  = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["dev.ratio"]][..2])
    ) %>%

@@

  arrange(cv_error)

View(fit_lasso)
```

@@

```{r}
n_alpha <- 101
mae   <- numeric(n_alpha)
alphas <- seq(0, 1, length.out = n_alpha)

@@

  print(i)

@@

plot(alphas, mae) # it seems that alpha = 1 gives the best results
```

# Green flag

@@

  # extract coefficients
  unnest(coefi_v)%>%

@@

# old code
## CV
```{r my_predict}
my_predict <- function(model, newdata, id){

@@

```{r my_CV}
my_CV <- function(df){

@@

## BSS
```{r my_BSS}
my_BSS <- function(df) regsubsets(Grade ~ ., data = df, nvmax = 7)
```

```{r extract_coef}
extract_coef <- function(BSS, BS) names(coef(BSS, BS))[-1]
```

```{r my_lm}
my_lm <- function(df, best_coef){

@@

```{r model fitting}
BSS <- tibble(target = course_obj) %>%

@@

```{r}
BSS_glance <- BSS %>% unnest(glanced) %>% select(-c(tidied, augmented)) %>%

@@

```{r}
course <- "HUM2021"

>>>>

```{r load, cache.lazy = TRUE}
load("App/Recommender System/topic_model_gb.RDATA")
load("Output/data_pillar_1.RDATA")
load("Output/course_current.RDATA")

@@

beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)
```

@@

```{r grade_ECTS}
d_transcript_augmented <- d_transcript_augmented %>%

@@

```{r student_GPA, cache = T}
student_GPA <- d_transcript_augmented %>%

@@

# Join student TP and GPA
```{r student_profile}
d_transcript_augmented <- d_transcript_augmented %>%

@@

  left_join(student_TP , by = c("Student ID", "time")) %>%

  nest(.key = profile, matches("GPA|Topic")) %>%

  mutate(profile = profile %>% map(as.matrix))
```

@@

```{r fit_lasso, cache = TRUE}
fit_lasso <- tibble(target = course_target) %>%

@@

```{r fit_lasso extract}
fit_lasso <- fit_lasso %>%

@@

  # Best model
  mutate(

    intercept  = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["a0"]][..2]),
    coefi      = list(m_lasso, lambda_min) %>% pmap(coef), # clearer output than pmap_dbl(~ ..1[["beta"]][,..2])
    df         = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["df"]][..2]),

    dev_null   = m_lasso %>% map_dbl(~ .[["nulldev"]]),
    dev_left   = list(m_lasso, index_best) %>% pmap_dbl(~deviance.glmnet(..1)[..2]),
    dev_unexpl = dev_null - dev_left,
    dev_ratio  = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["dev.ratio"]][..2])

  ) %>%

@@

  arrange(cv_error)
```

@@

```{r, cache = T}
n_alpha <- 101
mae   <- numeric(n_alpha)
alphas <- seq(0, 1, length.out = n_alpha)

@@

@@

# slight decrease in mae as alpha increase. Set alpha = 1 in my_cv.glmnet().
m <- lm(mae ~ alphas)
plot(alphas, mae)
abline(m, col = "red")
m %>% summary
```

# Preparation

@@

  # extract coefficients
  unnest(coefi_v) %>%

@@

# Save

```{r}
fit_lasso_app <- fit_lasso %>% select(target, cv)

d_transcript_augmented_app <- d_transcript_augmented %>%

  group_by(`Student ID`) %>% # only keep most recent profile of each student
  arrange(desc(time)) %>%
  slice(1) %>%

  select(`Student ID`, profile)

save(fit_lasso_app, d_transcript_augmented_app, file = "APP/Recommender System/grade_prediction.RDATA")
```

# Predict

```{r my_predict}
my_predict <- function(model, profile){

  predict.cv.glmnet(object = model, newx = profile, s = "lambda.min")

```{r}
course_ID <- c("COR1005", "HUM2005") # input$course
student_ID <- "6087587" # input$student

student_profile <- d_transcript_augmented_app %>%

  filter(`Student ID` == student_ID) %>%

  pull(profile) %>% .[[1]]

fit_lasso_app %>%

  filter(target %in% course_ID) %>%

  mutate(prediction = cv %>% map_dbl(my_predict, student_profile)) %>%

  mutate(flag_red    = prediction < 5.5,
         flag_orange = prediction %>% between(5.5, 7),
         flag_green  = prediction > 7)
```

# old code
## CV

```{r my_predict, eval = F}
my_predict <- function(model, newdata, id){

@@

```{r my_CV, eval = F}
my_CV <- function(df){

@@

## BSS
```{r my_BSS, eval = F}
my_BSS <- function(df) regsubsets(Grade ~ ., data = df, nvmax = 7)
```

```{r extract_coef, eval = F}
extract_coef <- function(BSS, BS) names(coef(BSS, BS))[-1]
```

```{r my_lm, eval = F}
my_lm <- function(df, best_coef){

@@

```{r model fitting, eval = F}
BSS <- tibble(target = course_obj) %>%

@@

```{r, eval = F}
BSS_glance <- BSS %>% unnest(glanced) %>% select(-c(tidied, augmented)) %>%

@@

```{r, eval = F}
course <- "HUM2021"
